---
title: "Assignment 3"
author: "Vienna Saccomanno"
date: "2/26/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Task 2: Truckee River Flow (2000-2016)

```{r packages}
#Attached packages
library(tidyverse)
library(tseries)
library(forecast)

```

```{r data}
#Load data
truckee<- read_csv("truckee_flow.csv")

#Convert data to time series data
truckee_ts<- ts(truckee$mean_va, frequency = 12, start = c(2000,1)) #Start in January, 2000
#truckee_ts
plot(truckee_ts)

#Decompse the time series
truckee_dc<-decompose(truckee_ts)
plot(truckee_dc)
```

###Task 2a. Description of the decomposed graphs
- The decomposed data show stationary, additive time series data with clear seasonality within each year.
- The overall trend seems to be decreasing over time
- There might be a longer ~5 year trend beyond the normal seasonality, but it not easily discernable. 
- There are no perceptible outliers in this dataset
- Based on the scale, residuals might be a big contributor (i.e. there is a lot of noise beyond seasonality)



###Task 2b. Forecasting for 5 years - exponential smoothing (Holt-Winters)
```{r forecast}

truckee_hw<-HoltWinters(truckee_ts)
#truckee_hw

#Smoothing parameters:
 #alpha: 0.2418713
 #beta : 0
 #gamma: 0.3384547

plot(truckee_hw) #Original data with the predication on top to check model accuracy (not yet forecasting)

#Future forecasting with holtwinters

truckee_forecast<- forecast(truckee_hw, h=60) #forecasting for 5 years, 60 months
plot(truckee_forecast, xlab = "Year", ylab = "Mean Discharge Value", sub = "Exponential smoothing of predictions about future discharge from the Truckee River")
title(main = list ("Exponential smoothing of predictions about future monthly averaged discharge from the Truckee River suggest that there will be a flatening trend in discharge from 2015-2020" [2]))

#Check the distribution of residuals
hist(truckee_forecast$residuals) #look pretty normal

```

```{r forecast_plot}

ggplot(truckee_forecast, aes(x=year_nu, ))

```

